Categorical and gradient aspects of wordlikeness\thanks{Thanks to Gene Buckley, Charles Yang, and audiences at NELS 43 for helpful comments.}

### 2012-12-07 1.tex
Added mention of Werker's group.
Added discussion of 1) early doubts about biuniqueness and 2) early phonological category (un)learning.

This argument against the distinction between morpheme structure constraints and phonological processes is quite similar to the famous argument (\citeyear{SPR}) against the morphophonemic/phonemic distinction.
The principle of biuniquness in vogue at that time separates neutralizing (morphophonemic) and non-neutralizing (phonemic) processes.
In Russian, obstruents participate in voice assimilation whether this neutralizes a phonemic distinction (\ref{rovs}a) or not (\ref{rovs}b): recall that there is no underlying /dʒ/ in Russian.
Under biuniqueness, there must be separate neutralizing and non-neutralizing variants of this process, however.
From this, \citeauthor{SPR} argues that biuniqueness (and the distinction between the morphophonemic and phonemic levels that follows from it) entails ``a significant increase in the complexity of the representation'' (24).
While \citet{Anderson2000} sketches an analysis which preserves biuniqueness without morphophonemic/phonemic duplication (see also \citealt{Kiparsky1985}), this requires further contested assumptions---contrastive underspecification (against which, see \citealt{Steriade1995}) and a Duke-of-York derivation.
This does not seem inconsistent with \citeauthor{SPR}'s claim that biuniquness imposes unnecessary additional complexities: under \citeauthor{Anderson2000}'s analysis the complexity is not a duplication, but rather a dependency on contentious theoretical assumptions.

@@

Typically-developing infants know their names and the names of their caretakers as early as 4 months of age \citep{Bortfeld2005,Mandel1995,Tincoff1999}.
While infants are born able to distinguish between monosyllabic and bisyllabic words, the youngest infants are thought to recognize syllables ``holistically'' rather than as segment sequences \citep{Bertoncini1981,Eimas1999,Jusczyk1987}.
As early as 6 months of age, infants know the visual referents of familiar words presented auditorily \citep{Bergelson2012}.
At 7.5 months, phonological representations are sufficiently detailed to allow infants to discriminate between words like \emph{cup} and mispronunciations like \emph{*tup} \citep{Jusczyk1995}.
By 8 months, infants are able to locate both familiar and novel words in continuous speech \citep{Jusczyk1997,Seidl2006}.

>>>>

This argument against the distinction between morpheme structure constraints and phonological processes is quite similar to the famous argument (\citeyear{SPR}) against the morphophonemic/phonemic distinction.\footnote{
    This is not to imply that \citeauthor{SPR} was the first to make this argument, or to otherwise disregard this distinction: similar ideas can be found in work by \citet{Bloch1941}, \citeauthor{Bloomfield1926} (\citeyear{Bloomfield1926}:160, \citeyear{Bloomfield1962}:5f.), \citet{Chao1934}, \citet[244f.]{Hamp1953}, and \citet[47f.]{Sapir1930a}, among others (see \citealt{Anderson1985} \emph{passim}).}
The principle of biuniquness in vogue at that time separates neutralizing (morphophonemic) and non-neutralizing (phonemic) processes.
In Russian, obstruents participate in voice assimilation whether this neutralizes a phonemic distinction (\ref{rovs}a) or not (\ref{rovs}b): recall that there is no underlying /dʒ/ in Russian.
Under biuniqueness, there must be separate neutralizing and non-neutralizing variants of this process, however.
From this, \citeauthor{SPR} argues that biuniqueness (and the distinction between the morphophonemic and phonemic levels that follows from it) entails ``a significant increase in the complexity of the representation\ldots{}an unwarranted complication which has no place in a scientific description of language'' (24).
While \citeauthor{Anderson1985} (\citeyear{Anderson1985}:110f., \citeyear{Anderson2000}) sketches an analysis which preserves biuniqueness without morphophonemic/phonemic duplication (see also \citealt{Kiparsky1985}), this requires further contested assumptions---contrastive underspecification (against which, see \citealt{Steriade1995}) and a Duke-of-York derivation.
This does not seem inconsistent with \citeauthor{SPR}'s claim that biuniquness imposes unnecessary additional complexities: under \citeauthor{Anderson2000}'s analysis the complexity is not a duplication, but rather a dependency on contentious theoretical assumptions.

@@

Typically-developing infants know their names and the names of their caretakers as early as 4 months of age \citep{Bortfeld2005,Mandel1995,Tincoff1999}.
While infants are born able to distinguish between monosyllabic and bisyllabic words, the youngest infants are thought to recognize syllables ``holistically'' rather than as segment sequences \citep{Bertoncini1981,Eimas1999,Jusczyk1987}.
As early as 6 months of age, infants know the visual referents of familiar words presented auditorily \citep{Bergelson2012}.
At 7.5 months, phonological representations are sufficiently detailed to allow infants to discriminate between words like \emph{cup} and mispronunciations like \emph{*tup} \citep{Jusczyk1995}.
By 8 months, infants are able to locate both familiar and novel words in continuous speech \citep{Jusczyk1997,Seidl2006}.
Perception of non-native phonetic contrasts for vowels and consonants begins to decline at this age \citep{Best1994,Polka1994,Werker1981,Werker1984,Werker1988}.
